SVG: The Paper

### 2022-04-19 Analysis/index.Rmd
figure update
minor
work on path length

# some more colours
#Isfahan2 = list(c("#d7aca1", "#ddc000", "#79ad41", "#34b6c6", "#4063a3"), c(4, 2, 3, 5, 1), colo

@@

If anything, our model is a little conservative: items are selected around 5% more often than we'd expect.

```{r, echo = TRUE}
mean(a_cut$acc - a_cut$b_bin)
```

@@

<TODO>

@@

# Shortest Path Analysis

@@

>>>>

# some more colours
col3 = c("#d7aca1", "#ddc000","#34b6c6",  "#79ad41", "#4063a3")

@@

@@

Here we can see that these candidate items are typically underweight.

@@

# Path Length Analysis

@@

- We will provide the model/simulation with the initial target selection.

```{r, fig.cap = "(*left*) Histogram comparing the empirical path lengths to simulations from our fitted model. Difference indicates the human path length - the simulated path length. (*right*) Histogram comparing the median path lengths per participant."}
path_lengths <- readRDS("scratch/path_lengths.rda") %>%
  rename(observer = "obs",
         condition = "cond",
         human = "human_path_length",
         model = "model_path_length") %>% 
  mutate(difference  = human - model) %>%
  pivot_longer(c(human, model, difference), names_to = "type", values_to = "path_length")

ggplot(path_lengths, aes(path_length, fill = type)) + 
  geom_histogram(bins = 25, alpha = 0.5, position = "identity") +
  geom_vline(xintercept = 0, linetype = 2) + 
  theme(legend.position = "bottom")  +
  scale_x_continuous("path length")  +
  scale_x_continuous("median path length") +
  scale_fill_manual(values = col3) -> plt1

path_lengths %>% group_by(observer, type) %>%
  summarise(path_length = median(path_length), .groups = "drop") %>%
  ggplot(aes(path_length, fill = type)) + 
  geom_histogram(bins = 25, alpha = 0.5, position = "identity") +
  geom_vline(xintercept = 0, linetype = 2) + 
  theme(legend.position = "bottom") +
  scale_x_continuous("median path length") +
  scale_fill_manual(values = col3) -> plt2

plt1 + plt2 + plot_layout(guides = "collect")  &
  theme(legend.position = 'bottom', legend.title = element_blank())
```

We can see that overall, the model is not making substantially longer paths through the items than our human participants. However, there is some variability in that some participants routinely select paths shorter than our model would, and others do not.

Perhaps this is related to predictability (i.e., how well the model can predict a participant's trial level behaviour)?

```{r fig.cap = "(*left*) A histogram showing the proportion of trials each participant managed a shorter path through the targets than the model's prediction. (*right*) Scatter plot showing the relationship between predictability (accuracy) and whether the model over or under estimates path length. Xs mark the outlier participants discussed above."}
path_lengths %>% filter(type == "difference") %>%
  mutate(shorter = path_length < 0) %>%
  group_by(observer, condition) %>%
  summarise(prop_shorter = mean(shorter), .groups = "drop") -> path_lengths_obs

path_lengths_obs %>%
  ggplot(aes(prop_shorter, fill = condition)) + 
  geom_histogram(alpha = 0.5, breaks = seq(0, 1, 0.2), position = "identity") +
  scale_x_continuous("prop. shorter than model", breaks = seq(0, 1, 0.2)) -> plt1

path_lengths <- full_join(path_lengths_obs, fit,
                          by = c("observer", "condition"))

ggplot(path_lengths, aes(accuracy, prop_shorter, colour = condition)) + 
  geom_point(aes(shape = is_outlier)) +
  geom_smooth(data = filter(path_lengths, is_outlier == 0), 
              method = "lm", formula = y ~ x, se = FALSE) + 
  scale_shape_manual(values = c(19, 4), guide = "none") + 
  scale_y_continuous("prop. shorter than model", breaks = seq(0, 1, 0.2)) +
  coord_cartesian(ylim = c(0, 1)) -> plt2

plt1 + plt2 + plot_layout(guides = "collect")  &
  theme(legend.position = 'bottom')

```{r}
